---
title: "figure_5_metabolites"
author: "wuxr"
date: "2024-12-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#fecal metabolite import data
```{r pressure, echo=FALSE}
fecal_metabolites <- read.table("metabolites data/fecal metabolites data.txt",header=T,sep="\t",check.names = FALSE)
fecal_metabolites_meta <- merge(metadata[,1:8],fecal_metabolites,by=c("Subject","Time"))
fecal_metabolite_name_group <- read.table("metabolites data/fecal_metabolites_name_group.txt",header=T,sep="\t")
```

##fecal metabolites PCOA(FIG 5A)
```{r pressure, echo=FALSE}
table <- fecal_metabolites_meta[,c(3,9:203)]
rownames(table) <- table$SampleID
table <- table[,-1]
table <- na.omit(table)

dis <- vegdist(table,method="bray",na.rm = TRUE)
pcoa <- ape::pcoa(dis,correction ="none")

#permanova
data <- subset(metadata,Time %in% c("W0","W4","W16"))
data <- data[data$SampleID %in% rownames(table),]
rownames(data)<- data$SampleID
perm <- adonis2(table~Treatment*Time, data = data, method="bray",permutations = 999)

##不同时间看组别之间的差异（W0：0.008，0.456； W4：0.0537，0.001；W16：0.2794，0.013）
data <- subset(metadata,Time=="W4")
tab <- table[rownames(data),] %>% na.omit()
data <- data[rownames(tab),]
adonis2(tab~Treatment, data = data, method="bray",permutations = 999)

#画图
plot  <- pcoa$vectors[,1:2]
plot <- data.frame(plot)
colnames(plot) <- c("PCoA1","PCoA2")
plot <- merge(plot,data,by='row.names')

eig <- as.numeric(pcoa$values[,1])
p <- perm$aov.tab$`Pr(>F)`[1]
R <- perm$aov.tab$R2[1]

ggplot(plot, mapping=aes(PCoA1, PCoA2,color=Treatment))+
    geom_point(size=3,alpha=0.7)+
    theme_classic()+stat_ellipse(data=plot,geom="path",aes(colour=Treatment),alpha=0.5)+scale_color_manual(values = group_color)+
    labs(x=paste("PCoA1(",format(100*eig[1]/sum(eig),digits=4),"%)",sep=""),y=paste("PCoA2(",format(100*eig[2]/sum(eig),digits=4),"%)",sep=""))+
    theme(legend.position = "none",axis.text = element_text(color="black"),strip.background = element_blank())+facet_grid(~Time)+ggtitle("Fecal metabolome PCoA")

```

##LMM
```{r pressure, echo=FALSE}
#time*group
W4 <- list()
W16 <- list()

for (i in 9:219){
    fit.lmer <- lmer(fecal_metabolites_meta[,i]~ Treatment*Time+Age+Gender+(1 | Subject),data = fecal_metabolites_meta)
    
    W4[[i]] <- summary(fit.lmer)$coefficients["TreatmentGroup2:TimeW4", "Pr(>|t|)"]
    W16[[i]] <- summary(fit.lmer)$coefficients["TreatmentGroup2:TimeW16", "Pr(>|t|)"]
}

fecal_metabolites_LMM <- data.frame(metabolites=colnames(fecal_metabolites_meta)[9:219],
                       W4=unlist(W4),
                       W16=unlist(W16),
                       stringsAsFactors = F)
```

###group1
```{r pressure, echo=FALSE}
table <- fecal_metabolites_meta
table[, 9:ncol(table)] <- lapply(table[, 9:ncol(table)], scale)
table <- subset(table,Treatment=="Group1")

W4 <- list()
W16 <- list()
W4_C <- list()
W16_C <- list()

for (i in 9:219){
    fit.lmer <- lmer(table[,i]~ Time+Age+Gender+(1 | Subject),data = table)
    
    W4[[i]] <- summary(fit.lmer)$coefficients["TimeW4", "Pr(>|t|)"]
    W16[[i]] <- summary(fit.lmer)$coefficients["TimeW16", "Pr(>|t|)"]
    W4_C[[i]] <- summary(fit.lmer)$coefficients["TimeW4", "Estimate"]
    W16_C[[i]] <- summary(fit.lmer)$coefficients["TimeW16", "Estimate"]
}

fecal_metabolites_LMM_g1 <- data.frame(metabolites=colnames(table)[9:219],
                       W4=unlist(W4),
                       W16=unlist(W16),
                       stringsAsFactors = F)

fecal_metabolites_LMM_g1_coef <- data.frame(metabolites=colnames(table)[9:219],
                       W4=unlist(W4_C),
                       W16=unlist(W16_C),
                       stringsAsFactors = F)
```

###group2
```{r pressure, echo=FALSE}
table <- fecal_metabolites_meta
table[, 9:ncol(table)] <- lapply(table[, 9:ncol(table)], scale)
table <- subset(table,Treatment=="Group2")

W4 <- list()
W16 <- list()
W4_C <- list()
W16_C <- list()

for (i in 9:219){
    fit.lmer <- lmer(table[,i]~ Time+Age+Gender+(1 | Subject),data = table)
    
    W4[[i]] <- summary(fit.lmer)$coefficients["TimeW4", "Pr(>|t|)"]
    W16[[i]] <- summary(fit.lmer)$coefficients["TimeW16", "Pr(>|t|)"]
    W4_C[[i]] <- summary(fit.lmer)$coefficients["TimeW4", "Estimate"]
    W16_C[[i]] <- summary(fit.lmer)$coefficients["TimeW16", "Estimate"]
}

fecal_metabolites_LMM_g2 <- data.frame(metabolites=colnames(table)[9:219],
                       W4=unlist(W4),
                       W16=unlist(W16),
                       stringsAsFactors = F)

fecal_metabolites_LMM_g2_coef <- data.frame(metabolites=colnames(table)[9:219],
                       W4=unlist(W4_C),
                       W16=unlist(W16_C),
                       stringsAsFactors = F)
```

###fecal metabolites heatmap(FIG 5C)
```{r pressure, echo=FALSE}
fecal_scfa_name <- c("Propionic acid","Valeric acid","Isobutyric acid","Acetic acid","Isovaleric acid","Heptanoic acid","Butyric acid","Caproic acid","Isocaproic acid","Ethylmethylacetic acid")

#P值矫正
test <- fecal_metabolites_LMM[1:195,]
test <- subset(test,!test$metabolites %in% fecal_scfa_name)
for (i in 2:ncol(test)){
  test[,i] <- p.adjust(test[,i],method="BH")
}
test <- subset(test, W4<0.25 | W16<0.25)

test2 <- fecal_metabolites_LMM_g1[1:195,]
test2 <- subset(test2,!test2$metabolites %in% fecal_scfa_name)
for (i in 2:ncol(test2)){
  test2[,i] <- p.adjust(test2[,i],method="BH")
}
test2 <- subset(test2, W4<0.05 | W16 < 0.05)
 
fecal_metabolites_sig <- test$metabolites
  
test3 <- fecal_metabolites_LMM_g2[1:195,]
test3 <- subset(test3,!test3$metabolites %in% fecal_scfa_name)
for (i in 2:ncol(test3)){
  test3[,i] <- p.adjust(test3[,i],method="BH")
}

#画图
G1_coef <- melt(fecal_metabolites_LMM_g1_coef,variable.name = "Time",value.name = "Coef")
G1_coef$Treatment <- "Group1"
G2_coef <- melt(fecal_metabolites_LMM_g2_coef,variable.name = "Time",value.name = "Coef")
G2_coef$Treatment <- "Group2"
all_coef <- rbind(G1_coef,G2_coef)

G1_pval <- melt(test2,variable.name = "Time",value.name = "qval")
G1_pval$Treatment <- "Group1"
G2_pval <- melt(test3,variable.name = "Time",value.name = "qval")
G2_pval$Treatment <- "Group2"
all_pval <- rbind(G1_pval,G2_pval)

plot_data <- merge(all_coef,all_pval,by=c("metabolites","Treatment","Time"))
plot_data <- merge(plot_data,fecal_metabolite_name_group,by.x="metabolites",by.y="Name")
plot_data$stars <- cut(plot_data$qval, breaks=c(-Inf, 0.001, 0.01, 0.05, Inf), label=c("***", "**", "*", ""))
plot_data$uni_name <- paste(plot_data$metabolites,plot_data$Group,plot_data$HMDB)

plot_data <- subset(plot_data,plot_data$metabolites %in% fecal_metabolites_sig)

plot_data <- plot_data %>% arrange(Group)
plot_data$uni_name <- factor(plot_data$uni_name, levels = rev(unique(plot_data$uni_name)))

ggplot(plot_data,aes(x=Time,y=uni_name,fill=Coef))+geom_tile()+facet_grid(~Treatment)+scale_fill_gradient2("Coefficients",low="#4d4e9e",mid="white",high="#f39f13")+labs(x="",y="")+geom_text(aes(label=stars), color="black",size=4)+theme_classic()+theme(axis.text = element_text(color="black",size=8),legend.title = element_text(size=8),legend.text = element_text(size=9,angle = 45, hjust = 1),strip.background = element_blank(),panel.grid = element_blank(),legend.position = "bottom")+guides(fill =  guide_colorbar(barwidth = 4, barheight = 0.5))+scale_y_discrete(position = "left")

```

#plasma metabolites import data
```{r pressure, echo=FALSE}
plasma_metabolites <- read.table("metabolites data/plasma metabolites data.txt",header=T,sep="\t",check.names = FALSE)
plasma_metabolites_meta<- merge(metadata[,1:8],plasma_metabolites,by=c("Subject","Time"))
plasma_metabolite_name_group <- read.table("metabolites data/plasma_metabolites_name_group.txt",header=T,sep="\t")
```


##plasma metabolites PCOA(FIG 5A)
```{r pressure, echo=FALSE}
table <- plasma_metabolites_meta
rownames(table) <- table$SampleID
table <- table[,8:ncol(table)]
table <- na.omit(table)
#table <- table[,fecal_metabolites_sig$Name]
dis <- vegdist(table,method="bray",na.rm = TRUE)
pcoa <- ape::pcoa(dis,correction ="none")

#permanova
data <- subset(metadata,Time %in% c("W0","W4","W16"))
data <- data[rownames(table),]
perm <- adonis2(table~Treatment*Time, data = data, method="bray",permutations = 999)

#不同时间看组别之间的差异（W0：0.0019，0.964； W4：0.00816，0.424；W16：0.00365，0.827）
data <- subset(metadata,Time=="W4")
tab <- table[rownames(data),] %>% na.omit()
data <- data[rownames(tab),]
adonis2(tab~Treatment, data = data, method="bray",permutations = 999)

#画图
plot  <- pcoa$vectors[,1:2]
plot <- data.frame(plot)
colnames(plot) <- c("PCoA1","PCoA2")
plot <- merge(plot,data,by='row.names')

eig <- as.numeric(pcoa$values[,1])
p <- perm$aov.tab$`Pr(>F)`[1]
R <- perm$aov.tab$R2[1]

ggplot(plot, mapping=aes(PCoA1, PCoA2,color=Treatment))+
    geom_point(size=3,alpha=0.7)+
    theme_classic()+stat_ellipse(data=plot,geom="path",aes(colour=Treatment),alpha=0.5)+scale_color_manual(values = group_color)+
    labs(x=paste("PCoA1(",format(100*eig[1]/sum(eig),digits=4),"%)",sep=""),y=paste("PCoA2(",format(100*eig[2]/sum(eig),digits=4),"%)",sep=""))+theme(legend.position = "none",axis.text = element_text(color="black"),strip.background =    element_blank())+facet_grid(~Time)+ggtitle("Plasma metabolome PCoA")
    #+annotate("text",x=30000,y=4500,parse=TRUE,label=paste('R:',format(R,digits=3)))+
    #annotate("text",x=30000,y=5500,parse=TRUE,label=paste('P:',p))+theme(legend.position = "none",axis.text = element_text(color="black"))
```

##LMM
```{r pressure, echo=FALSE}
#time*group
W4 <- list()
W16 <- list()

for (i in 9:219){
    fit.lmer <- lmer(plasma_metabolites_meta[,i]~ Treatment*Time+Age+Gender+(1 | Subject),data = plasma_metabolites_meta)
    
    W4[[i]] <- summary(fit.lmer)$coefficients["TreatmentGroup2:TimeW4", "Pr(>|t|)"]
    W16[[i]] <- summary(fit.lmer)$coefficients["TreatmentGroup2:TimeW16", "Pr(>|t|)"]
}

plasma_metabolites_LMM <- data.frame(metabolites=colnames(plasma_metabolites_meta)[9:219],
                       W4=unlist(W4),
                       W16=unlist(W16),
                       stringsAsFactors = F)
```

###group1
```{r pressure, echo=FALSE}
table <- plasma_metabolites_meta
table[, 9:ncol(table)] <- lapply(table[, 9:ncol(table)], scale)
table <- subset(table,Treatment=="Group1")

W4 <- list()
W16 <- list()
W4_C <- list()
W16_C <- list()

for (i in 9:219){
    fit.lmer <- lmer(table[,i]~ Time+Age+Gender+(1 | Subject),data = table)
    
    W4[[i]] <- summary(fit.lmer)$coefficients["TimeW4", "Pr(>|t|)"]
    W16[[i]] <- summary(fit.lmer)$coefficients["TimeW16", "Pr(>|t|)"]
    W4_C[[i]] <- summary(fit.lmer)$coefficients["TimeW4", "Estimate"]
    W16_C[[i]] <- summary(fit.lmer)$coefficients["TimeW16", "Estimate"]
}

plasma_metabolites_LMM_g1 <- data.frame(metabolites=colnames(table)[9:219],
                       W4=unlist(W4),
                       W16=unlist(W16),
                       stringsAsFactors = F)

plasma_metabolites_LMM_g2_coef <- data.frame(metabolites=colnames(table)[9:219],
                       W4=unlist(W4_C),
                       W16=unlist(W16_C),
                       stringsAsFactors = F)
```

###group2
```{r pressure, echo=FALSE}
table <- plasma_metabolites_meta
table[, 9:ncol(table)] <- lapply(table[, 9:ncol(table)], scale)
table <- subset(table,Treatment=="Group2")

W4 <- list()
W16 <- list()
W4_C <- list()
W16_C <- list()

for (i in 9:219){
    fit.lmer <- lmer(table[,i]~ Time+Age+Gender+(1 | Subject),data = table)
    
    W4[[i]] <- summary(fit.lmer)$coefficients["TimeW4", "Pr(>|t|)"]
    W16[[i]] <- summary(fit.lmer)$coefficients["TimeW16", "Pr(>|t|)"]
    W4_C[[i]] <- summary(fit.lmer)$coefficients["TimeW4", "Estimate"]
    W16_C[[i]] <- summary(fit.lmer)$coefficients["TimeW16", "Estimate"]
}

plasma_metabolites_LMM_g2 <- data.frame(metabolites=colnames(table)[9:219],
                       W4=unlist(W4),
                       W16=unlist(W16),
                       stringsAsFactors = F)

plasma_metabolites_LMM_g2_coef <- data.frame(metabolites=colnames(table)[9:219],
                       W4=unlist(W4_C),
                       W16=unlist(W16_C),
                       stringsAsFactors = F)
```

###plasma sig metabolites heatmap(FIG 5B)
```{r pressure, echo=FALSE}
plasma_scfa_name <- c("Acetic acid","Butyric acid","Caproic acid","Ethylmethylacetic acid","Isocaproic acid","Isovaleric acid","Propionic acid","Valeric acid")
#P值矫正
test <- plasma_metabolites_LMM[1:193,]
test <- subset(test,!test$metabolites %in% plasma_scfa_name)
for (i in 2:ncol(test)){
  test[,i] <- p.adjust(test[,i],method="BH")
}
test <- subset(test, W4<0.25 | W16<0.25)

plasma_metabolite_sig <- test$metabolites

test2 <- plasma_metabolites_LMM_g1[1:193,]
test2 <- subset(test2,!test2$metabolites %in% plasma_scfa_name)
for (i in 2:ncol(test2)){
  test2[,i] <- p.adjust(test2[,i],method="BH")
}

test3 <- plasma_metabolites_LMM_g2[1:193,]
test3 <- subset(test3,!test3$metabolites %in% plasma_scfa_name)
for (i in 2:ncol(test3)){
  test3[,i] <- p.adjust(test3[,i],method="BH")
}

#画图
G1_coef <- melt(plasma_metabolites_LMM_g1_coef,variable.name = "Time",value.name = "Coef")
G1_coef$Treatment <- "Group1"
G2_coef <- melt(plasma_metabolites_LMM_g2_coef,variable.name = "Time",value.name = "Coef")
G2_coef$Treatment <- "Group2"
all_coef <- rbind(G1_coef,G2_coef)

G1_pval <- melt(test2,variable.name = "Time",value.name = "qval")
G1_pval$Treatment <- "Group1"
G2_pval <- melt(test3,variable.name = "Time",value.name = "qval")
G2_pval$Treatment <- "Group2"
all_pval <- rbind(G1_pval,G2_pval)

plot_data <- merge(all_coef,all_pval,by=c("metabolites","Treatment","Time"))
plot_data <- merge(plot_data,plasma_metabolite_name_group,by.x="metabolites",by.y="Name")
plot_data$stars <- cut(plot_data$qval, breaks=c(-Inf, 0.001, 0.01, 0.05, Inf), label=c("***", "**", "*", ""))
plot_data$uni_name <- paste(plot_data$metabolites,plot_data$Group2,plot_data$HMDB)

plot_data <- subset(plot_data,plot_data$metabolites %in% test$metabolites)

plot_data <- plot_data %>% arrange(Group2)
plot_data$uni_name <- factor(plot_data$uni_name, levels = rev(unique(plot_data$uni_name)))

ggplot(plot_data,aes(x=Time,y=uni_name,fill=Coef))+geom_tile()+facet_grid(~Treatment)+scale_fill_gradient2("Coefficients",low="#4d4e9e",mid="white",high="#f39f13")+labs(x="",y="")+geom_text(aes(label=stars), color="black",size=4)+theme_classic()+theme(axis.text = element_text(color="black",size=8),legend.title = element_text(size=8),legend.text = element_text(size=9,angle = 45, hjust = 1),strip.background = element_blank(),panel.grid = element_blank(),legend.position = "bottom")+guides(fill =  guide_colorbar(barwidth = 4, barheight = 0.5))+scale_y_discrete(position = "left")

```

#SCFA related
##fecal SCFA
```{r pressure, echo=FALSE}
fecal_scfa_name <- c("Propionic acid","Valeric acid","Isobutyric acid","Acetic acid","Isovaleric acid","Heptanoic acid","Butyric acid","Caproic acid","Isocaproic acid","Ethylmethylacetic acid")

fecal_scfa_optimized_lmm <- subset(fecal_metabolites_optimised_LMM,fecal_metabolites_optimised_LMM$metabolites %in% fecal_scfa_name)
for (i in 2:ncol(fecal_scfa_optimized_lmm)){
  fecal_scfa_optimized_lmm[,i] <- p.adjust(fecal_scfa_optimized_lmm[,i],method="BH")
}

fecal_scfa_optimized_lmm_g1 <- subset(fecal_metabolites_optimised_LMM_g1,fecal_metabolites_optimised_LMM_g1$mettabolites %in% fecal_scfa_name)
for (i in 2:ncol(fecal_scfa_optimized_lmm_g1)){
  fecal_scfa_optimized_lmm_g1[,i] <- p.adjust(fecal_scfa_optimized_lmm_g1[,i],method="BH")
}

fecal_scfa_optimized_lmm_g2 <- subset(fecal_metabolites_optimised_LMM_g2,fecal_metabolites_optimised_LMM_g2$mettabolites %in% fecal_scfa_name)
for (i in 2:ncol(fecal_scfa_optimized_lmm_g2)){
  fecal_scfa_optimized_lmm_g2[,i] <- p.adjust(fecal_scfa_optimized_lmm_g2[,i],method="BH")
}
```

##plasma SCFA
```{r pressure, echo=FALSE}
plasma_scfa_name <- c("Acetic acid","Butyric acid","Caproic acid","Ethylmethylacetic acid","Isocaproic acid","Isovaleric acid","Propionic acid","Valeric acid")

plasma_scfa_optimized_lmm <- subset(plasma_metabolites_optimised_LMM,plasma_metabolites_optimised_LMM$metabolites %in% plasma_scfa_name)

for (i in 2:ncol(plasma_scfa_optimized_lmm)){
  plasma_scfa_optimized_lmm[,i] <- p.adjust(plasma_scfa_optimized_lmm[,i],method="BH")
}

plasma_scfa_optimized_lmm_g1 <- subset(plasma_metabolites_optimised_LMM_g1,plasma_metabolites_optimised_LMM_g1$metabolites %in% plasma_scfa_name)
for (i in 2:ncol(plasma_scfa_optimized_lmm_g1)){
  plasma_scfa_optimized_lmm_g1[,i] <- p.adjust(plasma_scfa_optimized_lmm_g1[,i],method="BH")
}

plasma_scfa_optimized_lmm_g2 <- subset(plasma_metabolites_optimised_LMM_g2,plasma_metabolites_optimised_LMM_g2$metabolites %in% plasma_scfa_name)
for (i in 2:ncol(plasma_scfa_optimized_lmm_g2)){
  plasma_scfa_optimized_lmm_g2[,i] <- p.adjust(plasma_scfa_optimized_lmm_g2[,i],method="BH")
}
```

##associations between fecal SCFA and blood biomarker
```{r pressure, echo=FALSE}
table <- fecal_metabolites_meta[,c(colnames(fecal_metabolites_meta)[1:8],fecal_scfa_name)]
table <- merge(table,metadata[,c(2,4,23:32)],by=c("Subject","Time"))
table[, 9:ncol(table)] <- lapply(table[, 9:ncol(table)], scale)

#group1
tab <- subset(table,Treatment=="Group1")

fecal_scfa_serum_corr_g1 <- data.frame(scfa = character(), serum=character(),coef=numeric(),pval = numeric(),low=numeric(),high=numeric(), stringsAsFactors=FALSE)

for (i in colnames(tab)[9:18]){
    for (j in colnames(tab)[19:28]){
    
    fit.lmer <- lmer(tab[,j] ~ tab[,i]+Age+Gender+(1 | Subject), data = tab)
    
    fecal_scfa_serum_corr_g1 <- rbind(fecal_scfa_serum_corr_g1, data.frame(scfa = i,serum=j,coef=summary(fit.lmer)$coefficients[2,1],pval = summary(fit.lmer)$coefficients[2,5],low=confint(fit.lmer)[4,1],high=confint(fit.lmer)[4,2], stringsAsFactors = FALSE))
    }
}
fecal_scfa_serum_corr_g1$group <- "Group1"
fecal_scfa_serum_corr_g1 <- fecal_scfa_serum_corr_g1 %>%
  group_by(scfa) %>%
  mutate(qval = p.adjust(pval, method = "BH"))

#group2
tab <- subset(table,Treatment=="Group2")

fecal_scfa_serum_corr_g2 <- data.frame(scfa = character(), serum=character(),coef=numeric(),pval = numeric(),low=numeric(),high=numeric(), stringsAsFactors=FALSE)

for (i in colnames(tab)[9:18]){
    for (j in colnames(tab)[19:28]){
    
    fit.lmer <- lmer(tab[,j] ~ tab[,i]+Age+Gender+(1 | Subject), data = tab)
    
    fecal_scfa_serum_corr_g2 <- rbind(fecal_scfa_serum_corr_g2, data.frame(scfa = i,serum=j,coef=summary(fit.lmer)$coefficients[2,1],pval = summary(fit.lmer)$coefficients[2,5],low=confint(fit.lmer)[4,1],high=confint(fit.lmer)[4,2], stringsAsFactors = FALSE))
    }
}
fecal_scfa_serum_corr_g2$group <- "Group2"

fecal_scfa_serum_corr_g2 <- fecal_scfa_serum_corr_g2 %>%
  group_by(scfa) %>%
  mutate(qval = p.adjust(pval, method = "BH"))
```

##associations between plasma SCFA and blood biomarker
```{r pressure, echo=FALSE}
table <- plasma_metabolites_meta[,c(colnames(plasma_metabolites_meta)[1:8],plasma_scfa_name)]
table <- merge(table,metadata[,c(2,4,23:32)],by=c("Subject","Time"))
table[, 9:ncol(table)] <- lapply(table[, 9:ncol(table)], scale)

#group1
tab <- subset(table,Treatment=="Group1")

plasma_scfa_serum_corr_g1 <- data.frame(scfa = character(), serum=character(),coef=numeric(),pval = numeric(),low=numeric(),high=numeric(), stringsAsFactors=FALSE)

for (i in colnames(tab)[9:16]){
    for (j in colnames(tab)[17:26]){
    
    fit.lmer <- lmer(tab[,j] ~ tab[,i]+Age+Gender+(1 | Subject), data = tab)
    
    plasma_scfa_serum_corr_g1 <- rbind(plasma_scfa_serum_corr_g1, data.frame(scfa = i,serum=j,coef=summary(fit.lmer)$coefficients[2,1],pval = summary(fit.lmer)$coefficients[2,5],low=confint(fit.lmer)[4,1],high=confint(fit.lmer)[4,2], stringsAsFactors = FALSE))
    }
}
plasma_scfa_serum_corr_g1$group <- "Group1"
plasma_scfa_serum_corr_g1 <- plasma_scfa_serum_corr_g1 %>%
  group_by(scfa) %>%
  mutate(qval = p.adjust(pval, method = "BH"))


#group2
tab <- subset(table,Treatment=="Group2")

plasma_scfa_serum_corr_g2 <- data.frame(scfa = character(), serum=character(),coef=numeric(),pval = numeric(),low=numeric(),high=numeric(), stringsAsFactors=FALSE)

for (i in colnames(tab)[9:16]){
    for (j in colnames(tab)[17:26]){
    
    fit.lmer <- lmer(tab[,j] ~ tab[,i]+Age+Gender+(1 | Subject), data = tab)
    
    plasma_scfa_serum_corr_g2 <- rbind(plasma_scfa_serum_corr_g2, data.frame(scfa = i,serum=j,coef=summary(fit.lmer)$coefficients[2,1],pval = summary(fit.lmer)$coefficients[2,5],low=confint(fit.lmer)[4,1],high=confint(fit.lmer)[4,2], stringsAsFactors = FALSE))
    }
}
plasma_scfa_serum_corr_g2$group <- "Group2"
plasma_scfa_serum_corr_g2 <- plasma_scfa_serum_corr_g2 %>%
  group_by(scfa) %>%
  mutate(qval = p.adjust(pval, method = "BH"))

```

###figure4B
```{r pressure, echo=FALSE}
plot_data <- rbind(fecal_scfa_serum_corr_g1,fecal_scfa_serum_corr_g2)
plot_data$site <- "Fecal"
plot_data2 <- rbind(plasma_scfa_serum_corr_g1,plasma_scfa_serum_corr_g2)
plot_data2$site <- "Blood"

figure4e_data <- rbind(plot_data,plot_data2)

variable <- c("TC_HDL_Ratio","TC","HDL","LDLm","TG","FG","HBA1C","Insulin","HOMA_IR")
test <- figure4e_data[figure4e_data$serum %in% variable,]

test$star <- cut(test$qval,breaks=c(-Inf, 0.001, 0.01, 0.05, Inf), label=c("***", "**", "*", ""))

test$serum <- factor(test$serum,levels = c("TC_HDL_Ratio","TC","HDL","LDLm","TG","FG","HBA1C","Insulin","HOMA_IR"))
test$scfa <- factor(test$scfa,levels = c("Acetic acid","Propionic acid","Butyric acid","Valeric acid","Isovaleric acid","Caproic acid","Isocaproic acid","Ethylmethylacetic acid","Isobutyric acid","Heptanoic acid"))
test$site <- factor(test$site,levels = c("Fecal","Blood"))

ggplot(test,aes(x=scfa,y=serum,fill=coef))+geom_tile(color="white")+scale_fill_gradient2("Coefficients",low="#2F7d77",mid="white",high="#9D6622")+labs(x="",y="")+theme_classic()+theme(axis.text = element_text(color="black",size=8),axis.text.x = element_text(angle=45,hjust = 1),legend.title = element_text(size=8),strip.background = element_blank(),panel.grid = element_blank(),legend.position = "right",axis.line = element_blank(),axis.ticks.x = element_blank())+guides(fill =  guide_colorbar(barwidth = 0.5, barheight = 4))+scale_y_discrete(position = "left")+geom_text(aes(label=star), color="black",size=4)+facet_grid(group~site)

```

###FIGS8 Scatter plots of gut SCFAs correlations with blood glucose and lipids
```{r pressure, echo=FALSE}
#blood scfa
table <- plasma_metabolites_meta[,c(colnames(plasma_metabolites_meta)[1:8],plasma_scfa_name)]
table <- merge(table,metadata[,c(2,4,23:32)],by=c("Subject","Time"))

for (i in colnames(table)[17:26]){
    p <- ggplot(table,aes(x=`Acetic acid`,y=table[,i]))+geom_point(shape=16,aes(color=Treatment),alpha=0.6,size=2)+geom_smooth(color="#CC9933",fill="#cc9933",method=lm)+scale_color_manual(values=c("#CC6666","#9999CC"))+theme_classic()+labs(y=i)+theme(axis.text = element_text(color="black",size=14),title = element_text(size=12),legend.position="none",strip.background = element_blank())+facet_grid(~Treatment,scales = "free")
    base::print(p)
    ggsave(p, file= paste("Acetic Acid_",i, ".pdf"),path="revise_figure/plasa_scfa_marker_scatter_plot/",width=5, height=4)
}

#fecal scfa
table <- fecal_metabolites_meta[,c(colnames(fecal_metabolites_meta)[1:8],fecal_scfa_name)]
table <- merge(table,metadata[,c(2,4,23:32)],by=c("Subject","Time"))

for (i in colnames(table)[19:28]){
  for (j in colnames(table)[9:18]){
    p <- ggplot(table,aes(x= table[,j],y=table[,i]))+geom_point(shape=16,aes(color=Treatment),alpha=0.6,size=2)+geom_smooth(color="#CC9933",fill="#cc9933",method=lm)+scale_color_manual(values=c("#CC6666","#9999CC"))+theme_classic()+labs(x=j,y=i)+theme(axis.text = element_text(color="black",size=14),title = element_text(size=12),legend.position="none",strip.background = element_blank())+facet_grid(~Treatment,scales = "free")
    base::print(p)
    ggsave(p, file= paste("Acetic Acid_",i, ".pdf"),path="revise_figure/plasa_scfa_marker_scatter_plot/",width=5, height=4)
  }
}

```


